A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2020-11-25 kobakian-cook.Rmd
slight wording in the intro

Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing the population in each administrative area [@TAAM]. This acknowledges that the number of residents can be different and also recognises that each area, or person within it is equally important.

This paper contains a discussion of Existing Mapping Practices. This is followed by details of the Algorithm. The implementation section discusses the algorithm in the `sugarbag` package. Finally, the use and benefits of animation are presented.

>>>>

Alternative mapping methods, like cartograms, allow increased understanding of the spatial distribution of a variable across the population, by fairly representing the population in each administrative area [@TAAM]. This acknowledges that the number of residents can be different and also recognises that each area, or person within it is equally important.

This paper contains a discussion of existing mapping practices. This is followed by details of the algorithm. The implementation section discusses the algorithm in the `sugarbag` package. Finally, the use and benefits of animation are presented.

### 2020-11-25 kobakian-cook.tex
slight wording in the intro

\abstract{%
Spatial distributions have been presented on alternative representations
of geography for many years. In modern times, interactivity and
animation have allowed alternative displays to play a larger role.
Alternative representations have been popularised by online news sites,
and digital atlases with a focus on public consumption. Applications are
increasingly widespread, especially in the areas of disease mapping, and
election results. The algorithm presented creates a display that uses
tessellated hexagons to represent a set of spatial polygons. It
allocates these hexagon in a manner that preserves the spatial
relationship of the geographic units, in light of their positions to
points of interest. The display showcases spatial distributions, by
emphasising the small geographical regions that are often difficult to
locate on geographic maps.
}

>>>>

\abstract{%
Spatial distributions have been presented on alternative representations
of geography, such as cartograms, for many years. In modern times,
interactivity and animation have allowed alternative displays to play a
larger role. Alternative representations have been popularised by online
news sites, and digital atlases with a focus on public consumption.
Applications are increasingly widespread, especially in the areas of
disease mapping, and election results. The algorithm presented creates a
display that uses tessellated hexagons to represent a set of spatial
polygons, and is implemented in the R package called sugarbag. It
allocates these hexagon in a manner that preserves the spatial
relationship of the geographic units, in light of their positions to
points of interest. The display showcases spatial distributions, by
emphasising the small geographical regions that are often difficult to
locate on geographic maps.
}
